Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-10 CAs_operads.tex
Corrections 3.3.1

Observe that each of these $n + 4$ trees avoids the left members of the

@@

\begin{Proposition} \label{prop:absorbing_normal_forms_type_B}
    For any two trees $\Tfr$ and $\Tfr'$ of the
    form~\eqref{equ:normal_forms_type_B} and $i \in [|\Tfr|]$, the
    normal form for the rewrite relation induced by $\Rew$ of
    $\Tfr \circ_i \Tfr'$ is a tree of the
    form~\eqref{equ:normal_forms_type_B}.
\end{Proposition}
\begin{proof}
    None of the trees of the form~\eqref{equ:normal_forms_type_A}
    contain the left or the right member of the rewrite
    rule~\eqref{equ:rew_1} generating the congruence relation
    $\CongrCAs{3}$. Hence, these trees are alone in their equivalence
    classes. Moreover, the trees of the
    form~\eqref{equ:normal_forms_type_B} contain the right member of
    the rewrite rule~\eqref{equ:rew_1} generating the congruence
    relation $\CongrCAs{3}$, so that the composition of such a tree
    with another tree is not alone in its equivalence class, and thus
    it does not belong to the family~\eqref{equ:normal_forms_type_A}.
\end{proof}
\medbreak

>>>>

Observe that each of these $n + 3$ trees avoids the left members of the

@@

\begin{Proposition} \label{prop:absorbing_normal_forms_type_B}
    For any two trees $\Tfr$ and $\Tfr'$, if one of them is of the
    form~\eqref{equ:normal_forms_type_B} and $i \in [|\Tfr|]$, then
    the normal form for the rewrite relation induced by $\Rew$ of
    $\Tfr \circ_i \Tfr'$ is a tree of the
    form~\eqref{equ:normal_forms_type_B}.
\end{Proposition}
\begin{proof}
    None of the trees of the form~\eqref{equ:normal_forms_type_A}
    contain the left or the right member of the rewrite
    rule~\eqref{equ:rew_1} generating the congruence relation
    $\CongrCAs{3}$. Hence, these trees are alone in their equivalence
    classes. Moreover, the trees of the
    form~\eqref{equ:normal_forms_type_B} contain the right member of
    the rewrite rule~\eqref{equ:rew_1} generating the congruence
    relation $\CongrCAs{3}$, so that the composition of such a tree
    with another tree is not alone in its equivalence class, and thus
    it does not belong to the family~\eqref{equ:normal_forms_type_A}.
\end{proof}
\medbreak
